Results Analysis

### 2024-04-25 analysis/resultsAnalysis.Rmd
Updated analysis plots
Also simplified some analysis code.

prominentPPC
```
Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```
Get how many prominent journals offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))

# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  summarise(count = n())
```

Inspect PPC types at prominent journals
```{r}
# Counts for all types of PPC, commentary only, and letters only
promAllTypes <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  summarise(n())

promCommentary <- dj_prominent %>%
  filter(ppc_name == "Commentary") %>%
  summarise(n())

promLetters <- dj_prominent %>%
  filter(ppc_name == "Letters") %>%
  summarise(n())

# These numbers will be used in percentage calculations for limits
promAllTypes # Total number of PPC options found in prominent journals
promCommentary # Total number of 'Commentary' options
promLetters # Total number of 'Letters' options
```
Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPEtable <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPEtable
```

@@

randomPPC_CI
```
Get how many randomly selected journals offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))

# Return count
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  summarise(count = n())
```

Get the names of the randomly samples journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Inspect PPC types at randomly selected journals
```{r}
randomTypes <- dj_random %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(count = n()) %>%
  ungroup()

randomTypes
```

Inspect the COPE status of randomly selected journals with and without PPC policies
```{r}
randCOPEtable <- dj_random %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

randCOPEtable
```

@@

## Calculations for Table 1: Prominent journals

@@

## Calculations for Table 2: Randomly selected journals

@@

>>>>

prominentPPC
```
Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```
Get names for prominent journals that offered more than one type of PPC
```{r}
# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Inspect PPC types at prominent journals
```{r}
table(dj_prominent$ppc_name)
```
Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPE
```

@@

randomPPC_CI
```
Get names for randomly selected journals that offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Inspect PPC types at randomly selected journals
```{r}
table(dj_random$ppc_name)
```

Inspect the COPE status of randomly selected journals with and without PPC policies
```{r}
randomCOPE <- dj_random %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

@@

## Calculations for Table 1: PPC limits in prominent journals

@@

## Calculations for Table 2: PPC limits in randomly selected journals

@@

# FIGURES
Boxplot of quantitative length limits
```{r}
quantLength <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_length),
         ppc_length != "NOT STATED",
         ppc_length != "Qualitative") %>%
 mutate(Length = as.numeric(ppc_length))

quantLength %>%  
 ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
 geom_violin(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.1,
             alpha = 0.8) + 
 scale_fill_brewer(palette = "Set2") +
 scale_color_brewer(palette = "Set2") +
 coord_flip() +
 theme_bw() +
 labs(title = "All stated quantitative length Limits", x = "Post-publication critique type", y = "Length limits (words)")

```
Boxplot of quantitative time limits
```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

quantTime %>%  
 ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
 geom_boxplot(
    color = "black",
    fill = "lightblue",
    alpha = 0.5
 ) +
 geom_jitter(width = 0.2) + 
 scale_fill_brewer(palette = "Set2") +
 scale_color_brewer(palette = "Set2") +
 coord_flip() +
 theme_bw() +
 labs(title = "All stated quantitative time limits", x = "Post-publication critique type", y = "Time limits (weeks)")
```
### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*

```{r, echo = FALSE, message=FALSE}
# Filter and transform restrictions for ppc_length
prominent_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and transform restrictions for ppc_time
prominent_time_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  prominent_length_data %>% mutate(Code = "Length"),
  prominent_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
  theme(axis.text.x = element_text(size = 7))

# Create the second graph
graph2 <- dj_prominent %>%
  filter(ppc_type == "A") %>% # Keeps only first entry for each journal
  filter(!is.na(has_ppc)) %>% # Remove journal rows with no (NA) PPC options 
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes Explicit',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black",
           width = 0.8) +
  theme_bw() +
  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph2 + graph1
combined_plots

#ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
```

### *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
```{r echo=FALSE, message=FALSE}
# Create and combine restriction statement graphs with PPC acceptance (random sample)

# Filter and process data for ppc_length
random_length_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
random_time_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  random_length_data %>% mutate(Code = "Length"),
  random_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
  theme(axis.text.x = element_text(size = 7))

# Create the second graph
graph3 <- d_journals %>%
  filter(sample_id == "random" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes Explicit',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black",
           width = 0.8) +
  theme_bw() +
  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph3 + graph4
combined_plots

#ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
```
